### 2013-08-13 Tex/chapters/appendix.tex
Evolution des RNG kurz erläutert
Kontinuität: c jetzt immer klein
Anhang mit Ergebnissen für alpha=0, normierung mit K

\section{Finite Size Effects at the Example of the Specific Heat}
\label{appendix:finiteSizeEffects}
    In fig. \ref{fig:smeared_out_appendix} the specific heat
    \begin{equation}
        C = \frac{N}{T^2}\avg{\avg{E^2} - \avg{E}^2}
    \end{equation}
    is plotted for different system sizes. The finite size effects are obvious.
    The divergence is finite, and gets shallower with smaller \(L\). Besides
    the maximum moves away from the critical temperature with smaller \(L\).
    \begin{figure}[htbp]
        \centering
        \includegraphics[width=0.45\textwidth]{plots/Specific_Heat_0}
        \caption[Finite Size Effects by Example of the Specific Heat]
        {
            Effects of different system sizes at \(\sigma = 0\). Dotted lines
            are guides to the eye.
        }
        \label{fig:smeared_out_appendix}
    \end{figure}

\section{Effect of $\sigma$ on the RNG}
\label{appendix:RNGDisplacement}
    todo: RNG Bilder mit versch. sigma

>>>>

\section{Appendix}
\subsection{Finite Size Effects at the Example of the Specific Heat}
\label{appendix:finiteSizeEffects}
    In fig. \ref{fig:smeared_out_appendix} the specific heat
    \begin{equation}
        c = \frac{N}{T^2}\avg{\avg{E^2} - \avg{E}^2}
    \end{equation}
    is plotted for different system sizes. The finite size effects are obvious.
    The divergence is finite, and gets shallower with smaller \(L\). Besides
    the maximum moves away from the critical temperature with smaller \(L\).
    \begin{figure}[htbp]
        \centering
        \includegraphics[width=0.45\textwidth]{plots/Specific_Heat_0}
        \caption[Finite Size Effects by Example of the Specific Heat]
        {
            Effects of different system sizes at \(\sigma = 0\). Dotted lines
            are guides to the eye.
        }
        \label{fig:smeared_out_appendix}
    \end{figure}

\subsection{Course of the Critical Temperature $T_c$ with Fixed Coupling Constants $J$}
\label{appendix:fixedCoupling}
    A quick analysis of this model with fixed coupling constants \(J = 1\)
    (i.e.\ \(\alpha=0\)) is performed. The results are displayed in fig. \ref{fig:Tc_deg_A0}.
    The jump from \(\sigma=0\) to \(\sigma>0\) does not disappear as in fig. \ref{fig:Tc_deg}
    for variable \(J\) (i.e.\ \(\alpha=0.5\)). This suggests, that the
    disappearance of the jump is a random special case for the function
    \(J_{ij}=e^{\alpha(1-d)}\).\\
    The simulations were carried out on \(L \in \{16,32,64\}\) lattices
    for a subset of the \(\sigma\) and \(T\) used in the previous simulation.
    Every other parameter was kept. Also note that the degree \(K\) is
    the same used in \ref{fig:Tc}\subref{sfig:deg:RNG}\subref{sfig:deg:GG}
    because it is obviously independent of \(J\).
    \begin{figure}[htbp]
        \centering
        \subfigure[][]
        {
            \label{sfig:Tc:RNG_A0}
            \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_A0}
        }
        \subfigure[][]
        {
            \label{sfig:Tc:GG_A0}
            \includegraphics[width=0.45\textwidth]{plots/GG_Tc_A0}
        }

        \subfigure[][]
        {
            \label{sfig:Tc_norm_deg:RNG_A0}
            \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_norm_deg_A0}
        }
        \subfigure[][]
        {
            \label{sfig:Tc_norm_deg:GG_A0}
            \includegraphics[width=0.45\textwidth]{plots/GG_Tc_norm_deg_A0}
        }

        \caption[Critical Temperature and Critical Temperature Normalized by Degree of the Graph for Fixed Coupling Constants $J=1$]
        {
            Top: Critical Temperature \(T_c\) of the graph over different
            disorder parameters \(\sigma\) with fixed coupling constants \(J=1\) for
            \subref{sfig:deg:RNG} the RNG and
            \subref{sfig:deg:GG} the GG.\\
            Bottom: Critical temperatures normalized by degree \(K\) over
            different disorder parameters \(\sigma\) with fixed coupling constants \(J=1\) for
            \subref{sfig:Tc_norm_deg:RNG} the RNG and
            \subref{sfig:Tc_norm_deg:GG} the GG.
        }
        \label{fig:Tc_deg_A0}
    \end{figure}\\

### 2013-08-13 Tex/chapters/results.tex
Anmerkung zum chi max fit
Anhang mit Ergebnissen für alpha=0, normierung mit K

@@

@@

    between the RNG and the GG.

>>>>

    Note that the maximum of the measured \(\chi\). Because there were
    many measurements in the vicinity of \(T_c\) (compare fig. \ref{sfig:gettingCrit:s_1_sus}),
    this should give a reasonable estimate, without the need to
    interpolate a maximum.

@@

    Note that \(K\) is independent of \(L\) because of the periodic boundary.

@@

    between the RNG and the GG. But the elimination of the jump is
    unfortunately random and probably caused by a lucky choice of the
    function, which determines the coupling constants \(J\). As proof for
    this claim in appendix \ref{appendix:fixedCoupling} the same analysis
    is performed for a model with fixed \(J\). There the jump gets narrower
    but is still existent. Anyway, the degree seems to have an impact on
    the critical temperature \(T_c\) but it is not a trivial one.
